Spitzer, Gaia and the Potential of the Milky Way

### 2013-07-31 text/paper1/paper.tex
getting prose-y

\documentclass{emulateapj}
%\documentclass[preprint]{aastex}

@@

[Ok, there is a question as to whether we even want to say something like the below...?]

@@

This paper presents an algorithm for measuring the Galactic potential
that anticipates combined data from the Spitzer and Gaia satellite
missions that promise precise, full phase-space measurements of RR
Lyrae stars in the halo of our Galaxy. When applied to a sample of 100
stars -- with realistic observational errors -- sampled from the
\cite{law10} N-body simulation of the destruction of the Sgr dwarf
satellite, the method recovers the shape and orientation of the dark
matter potential XXX. This success provides strong motivation for 1)
further theoretical work to [...], 2) an investigation of the power of
using multiple, complimentary debris structures (e.g., with different
morphologies and orientations) in building a comprehensive picture of
the Galactic mass distribution, and 3) a Spitzer survey of RR Lyrae
stars in debris structures around the Milky Way to get precise
distances to combine with near-future Gaia velocity data.

>>>>

%\documentclass{emulateapj}
\documentclass[preprint]{aastex}

@@

[KVJ: Ok, there is a question as to whether we even want to say something like the below...?]

@@

This paper presents an algorithm for measuring the Galactic potential
that anticipates combined data from the Spitzer and Gaia satellite
missions that promise precise, full phase-space measurements of RR
Lyrae stars in the halo of our Galaxy. When applied to a sample of 100
stars (with realistic observational errors) sampled from the
\cite{law10} N-body simulation of the destruction of the Sgr dwarf
satellite, the method recovers the shape and orientation of the dark
matter potential XXX. This success provides strong motivation for 1)
further theoretical work to develop a robust generative model (and therefore likelihood) that utilizes the concepts demonstrated by the \emph{Rewinder}, 2) an investigation of the power of
using multiple, complimentary debris structures (e.g., with different
morphologies and orientations) in building a comprehensive picture of
the Galactic mass distribution, and 3) a Spitzer survey of RR Lyrae
stars in debris structures around the Milky Way to get precise
distances to combine with near-future Gaia velocity data. We conclude by noting that this method is complimentary to the orbit fitting algorithm presented in \citet{sanders13b} by favoring warmer, more massive debris structures like Sgr. By developing and comparing independent methods for measuring the potential of the Milky Way, we will begin to develop a deeper understanding of the vast structures of dark matter that permeate the universe. [Yea, the last sentence I wrote in the late night and am probably delirious...]
